---
title: "Interact with and investigate Australia's 2020 Coronavirus Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interact with and investigate Australia's 2020 Coronavirus Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Welcome

Welcome to the 'ozcovid' package! The purpose of this package is to allow you - the user - to interact with and investigate Australia's 2020 coronavirus data. The package aims to do this in two main ways - a shiny application called 'Coronavirus in Australia' and a dataset called 'oz_covid_data'.

## Setup 

First you will need to install and load the package. See below:

```{r setup, eval=FALSE}
#install package
devtools::install_github("etc5523-2020/r-package-assessment-mayunk264")

#load package
library(ozcovid)
```

## Functions and Dataset within Package

### load_app() function

The load_app() function is the centrepiece of the package. When executed, the function will return a Shiny application entitled 'Coronavirus in Australia'.

There are three main sections of the application:

1. Confirmed Cases by state: a graph displaying confirmed coronavirus cases by state over time where the user is able to select their state of interest.
2. Coronavirus Summary Table: a table which displays daily and cumulative coronavirus confirmed cases, deaths and recoveries by date where the user is able to select their date of interest.
3. Deaths In Victoria: an interactive graph of Victoria's coronavirus-related deaths where the user is able to click on a data point of their choice which in turn generates a sentence describing the date and the deaths that occurred on that date in Victoria.

The application can be executed like so:

```{r launch-app, eval=FALSE}
#launch the Shiny application
ozcovid::launch_app()
```

### oz_covid_data dataset

The 'oz_covid_data' dataset summarises Australia's 2020 coronavirus data. 

The dataset is a processed version of Rami Krispin's coronavirus' dataset from the ['coronavirus' package](https://github.com/RamiKrispin/coronavirus.). If the dataset looks familiar to you, it is because it is inspired by the 'Coronavirus Summary Table' from the 'Coronavirus in Australia' Shiny application.

The dataset contains a date variable and corresponding variables for total 'Daily Confirmed' coronavirus cases, 'Daily Death' related to coronavirus, 'Daily Recovered' coronavirus cases, 'Cumulative Confirmed' coronavirus cases, 'Cumulative Deaths' related to coronavirus and 'Cumulative Recovered' coronavirus cases. The 'date' column is of type <date> and the remaining columns are of type <int>.

The dataset can be generated like so:

```{r oz-covid-data, eval=FALSE}
#generate the oz_covid_data dataset
ozcovid::oz_covid_data
```

### stateSelectInput() and vicRenderText() functions

The 'stateSelectInput' and 'vicRenderText' functions are functions that contain refactored code from the user interface and server logic of the Shiny application 'Coronavirus in Australia'

These two functions - when executed in the console - will not generate anything meaningful for a user looking to only interact with the Shiny app or dataset. However, if a user is looking to use the code underlying the function to assist in the generation of their own Shiny application, the code may be of use.

## Issues

If you have any issues you would like to submit, please do so in the [Issues tab of the package's GitHub repository](https://github.com/etc5523-2020/r-package-assessment-mayunk264/issues).

